A Data-Driven Framework for Neural Field Modelling

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
Changes in section 3.2.1. to better justify eliminating the high frequency components in the field reconstruction.

Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}. In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line. The actual parameter values, the mean parameter estimates, standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries in the table show results from Experiment II. The biases show the percentage differences between the actual values and the mean parameter estimates. For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters. However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates. We attribute this small bias to the disparity between the actual field and the smoother estimated field from the decomposition.

>>>>

Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}. In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line. The actual parameter values, the mean parameter estimates, standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries in the table show results from Experiment II. The biases show the percentage differences between the actual values and the mean parameter estimates. For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters. However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates. We attribute this small bias to the loss of the high frequency components in the smoother estimated field with respect to the actual field. These results thus indicate that choosing to limit the frequency content of the reconstructed neural field has only minor effects on the accuracy of the estimated kernel while allowing for significant gains in the computational demand.
